Response to the defense feedback

### 2021-06-14 Chapter-4/Chapter-4.tex
Updates from Overleaf

\section{Problem}
In Chapter~\ref{chapter3}, we present a method to identify address-based side-channel leakage sites in cryptography libraries ~\cite{Osvik2006,Gullasch:2011:CGB:2006077.2006784,203878,10.1007/978-3-540-45238-6_6}. However, many reported leakage sites are not patched by developers. Recent work on side-channel vulnerabilities identification~\cite{203878,217537,Wichelmann:2018:MFF:3274694.3274741,Brotzman19Casym,236338,182946} also faced the same situation. For example, DATA~\cite{217537} reports 2,248 potential leakage sites for the RSA implementation in OpenSSL 1.1.0f\@. Further analysis shows 1,510 leaks can be dismissed. But that leaves 460 data-access leaks and 278 control-flow leaks. Many of these vulnerabilities have not been fixed by developers for a variety of reasons.

>>>>

\section{Problem}
In Chapter~\ref{chapter3}, we present a method to identify address-based side-channel leakage sites in cryptography libraries ~\cite{Osvik2006,Gullasch:2011:CGB:2006077.2006784,203878,10.1007/978-3-540-45238-6_6}. However, many reported leakage sites are not patched by developers. Recent work on side-channel vulnerability identification~\cite{203878,217537,Wichelmann:2018:MFF:3274694.3274741,Brotzman19Casym,236338,182946} also faced the same situation. For example, DATA~\cite{217537} reports 2,248 potential leakage sites for the RSA implementation in OpenSSL 1.1.0f\@. Further analysis shows 1,510 leaks can be dismissed. But that leaves 460 data-access leaks and 278 control-flow leaks. Many of these vulnerabilities have not been fixed by developers for a variety of reasons.
